\documentclass[margin,line]{res}

\usepackage{hyperref}
\usepackage{color}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}
%\vspace{-0.5in}
\name{\Huge Ashish Upadhyay \vspace*{.1in}}

\begin{resume}
\vspace{-0.1in}
\section{\sc Contact Information}
%\vspace{.05in}
\begin{tabular}{@{}p{2in}p{3in}}          
126 Auchinyell Road   & {\it Contact:} a.upadhyay@rgu.ac.uk, +44-7427970754 \\         
Aberdeen & {\it Google Scholar:} {\href{https://scholar.google.co.in/citations?view_op=list_works&hl=en&user=aUwP8DAAAAAJ}{Ashish Upadhyay}}\\       
United Kingdom & {\it LinkedIn:} {\href{https://www.linkedin.com/in/ashishu007/}{https://linkedin.com/in/ashishu007/}} \\     
AB10 7EB  & {\it GitHub: }\href{https://github.com/panditu2015}{https://github.com/panditu2015} \\     
\end{tabular}

\vspace{-0.1in}
\section{\sc Interests}
Machine (Deep) Learning, Natural Language Processing.

\vspace{-0.1in}
\section{\sc Education}
{\bf International Institute of Information Technology}, Naya Raipur (IIIT-NR), India
%{\em Department of Computer Science and Engineering}
\begin{list1}
\item[] B.Tech, Computer Science and Engineering, May 2019 - Expected (88.2\%)
\end{list1}
\vspace{-0.1in}
{\bf DAV Public School}, Moonidih - Dhanbad, Jharkhand, India\\
\vspace*{-.5cm}
\begin{list1}
\item[] Intermediate - AISSCE, May 2015 (93.8\%)
\end{list1}
\vspace{-0.1in}
{\bf Toolika Public School}, Ghazipur, Uttar Pradesh, India\\
\vspace*{-.5cm}
\begin{list1}
\item[] Matriculation - AISSE, May 2013 (9.8 CGPA)
\end{list1}

\section{\sc Publications}
Shrivishal Tripathi, {\bf Ashish Upadhyay}, Shashank Kotyan, and Sandeep Yadav. {\em ``Analysis and Comparison of Different Fuzzy Inference Systems Used in Decision Making for Secondary Users in Cognitive Radio Network."} Wireless Personal Communications (2018): 1-34. \textcolor{blue}{\href{https://doi.org/10.1007/s11277-018-6075-9
}{[DOI]}}
\vspace{.1cm}\\
{\bf Ashish Upadhyay}, Kushashwa Ravi Shrimali, Anupam Shukla,
{\em ``UAV-Robot Relationship for Coordination of Robots on a Collision Free Path"}, Procedia Computer Science, Volume 133, 2018, Pages 424-431, ISSN 1877-0509. \textcolor{blue}{\href{https://doi.org/10.1016/j.procs.2018.07.052}{[DOI]}}

\vspace{-0.1in}
\section{\sc Scholarships}
{\bf Studentship at RGU}: \pounds 1231 per month to support my expenses during final semester internship.\\
{\bf Studentship at RGU}: \pounds 1000 per month to support my expenses during summer internship.\\
{\bf Chief Minister Scholarship at IIIT-NR}: Waiver of 1st year tuition fees of Bachelors degree.


\vspace{-0.1in}
\section{\sc Internships}
{\bf Robert Gordon University (RGU),} Aberdeen, United Kingdom\\
{\bf Source Classification of Oil and Gas Compliance Documents}

\vspace{-.3cm}
{\em Guide: Dr. Stewart Massie, Senior Research Fellow, RGU} \hfill {\bf December 2018 - Present}\\
\vspace*{-.4cm}
\begin{list2}
\item[-] Classified Oil and Gas compliance documents based on their sources. First used TF-IDF, Count Vectors as the features. Applied feature selection techniques to reduce the dimensionality from 160k to 1k of the feature vector.
\item[-] Identified problem specific engineered features and compared them with the TF-IDF and Count Vectors for better results. Achieved 97.32\% cross validation accuracy.
\item[-] Successfully classified highly imbalanced dataset with good accuracy as well as Macro F1 score.
\end{list2}

\vspace{-0.1in}

{\bf National Informatics Centre (NIC),} Chhattisgarh, India\\
{\bf Pronunciation Similarity Matching using Deep Learning}

\vspace{-.3cm}
{\em Guide: Dr. Muneendra Ojha, Asst. Professor, CSE, IIIT-NR} \hfill {\bf August 2018 - December 2018}\\
\vspace*{-.4cm}
\begin{list2}
\item[-] Developed a Client-server model for pronunciation matching to be used by the local students and teachers of Chhattisgarh to improve their English pronunciation by practicing.
\item[-] Used the {\bf MFCC Technique} for feature extraction from the speech signal by converting speech into an image. Then used that feature matrix to train a {\bf CNN} Network. Used Keras and Tensorflow for the development of DL model.
\end{list2}

\vspace{-0.1in}

{\bf Robert Gordon University (RGU),} Aberdeen, United Kingdom\\
{\bf Application of Machine Learning and Optimization in Supply-Chain Management}

\vspace{-.3cm}
{\em Guide: Prof. John McCall, Head of CSDM School, RGU} \hfill {\bf May 2018 - July 2018}\\
\vspace*{-.4cm}
\begin{list2}
\item[-] Developed an algorithm for the automation of tasks for creating jobs of picking items from different places in Scotland and minimizing the number of trucks used.
\item[-] Used Python (Libraries: {\bf Sklearn and Pandas}) for implementing the {\bf k-Means Clustering} and Bin Packing Algorithms.
\end{list2}

\vspace{-.1cm}
{\bf Indian Institute of Information Technology \& Management,} Gwalior (IIITM-G), India\\
{\bf UAV-Robot Relationship for Coordination of Robots on a Collision Free Path}

\vspace{-.3cm}
{\em Guide: Prof. Anupam Shukla, Professor, ICT, IIITM-G} \hfill {\bf December 2017}\\
\vspace*{-.4cm}
\begin{list2}
\item[-] Developed an algorithm using {\bf A*} and {\bf PRM} for the coordination of multiple robots on a collision free path using the bird eye view of an UAV. \textcolor{blue}{\href{https://doi.org/10.1016/j.procs.2018.07.052}{[Published Paper]}}.
\end{list2}

\vspace{-.1in}
\section{\sc Academic Projects}


% \vspace{-.1in}
{\bf Twitter Sentiment Analysis of the Policies of Modi Government}
\begin{list2}
\item[-] Used {\bf Distant Supervision} for dataset creation. Collected around 1M tweets on the various topics like GST \& Demonetization. Labeled them in three classes (positive, negative \& neutral).
\item[-] Used Unigram technique for feature extraction. Library Used {\bf NLTK}.
% \item[-] Used this labeled dataset for analyzing the performance of government. 
\textcolor{blue}{\href{https://github.com/panditu2015/Sentiment-Analysis}{[GitHub]}}
\end{list2}

\vspace{-.1in}
{\bf Human Facial Expression Recognition using Deep Learning}
\vspace{-.4cm}

{\em Guide: Dr. Santosh Kumar, Asst. Professor, CSE, IIIT-NR} \hfill {\bf April 2018}\\

\vspace*{-.3cm}
\begin{list2}
\item[-] Classified Human Facial Expression in 7 different classes (expressions) using {\bf Convolutional Neural Network}. Libraries used: {\bf OpenCV and Keras}. Used Kaggle's FER Dataset.
\end{list2}

\vspace{-.1in}
{\bf Handwritten Character Recognition of Devnagri Letters using Deep Learning}
\begin{list2}
\item[-] Recognized Handwritten Devnagri Characters using CNN on a dataset from \textcolor{blue}{\href{https://archive.ics.uci.edu/ml/datasets/Devanagari+Handwritten+Character+Dataset}{UCI Machine Learing Repository}}. Classified characters into 46 classes. \textcolor{blue}{\href{https://github.com/panditu2015/DL-Character-Recogntion}{[GitHub]}}
\end{list2}

\vspace{-.1in}
{\bf Coordination of Intelligent Agents on a Pre-Defined Path using A* and PSO}

\vspace{-.3cm}
{\em Guide: Dr. Muneendra Ojha, Asst. Professor, CSE, IIIT-NR} \hfill {\bf August 2017 - November 2017}\\
\vspace*{-.4cm}
\begin{list2}
\item[-] Developed an algorithm for multi-agent coordination using A* and PSO. Extended this project to implement the developed algorithm in real world. Simulated the algorithm in Gazebo. \textcolor{blue}{\href{https://github.com/panditu2015/Intelligent-Agents-Coordination}{[GitHub]}}
\end{list2}


\vspace{-.1in}
{\bf Analysis of Different FISs used in Decision Making for Secondary Users in CRN}

\vspace{-.3cm}
{\em Guide: Dr. Shrivishal Tripathi, Asst. Professor, ECE, IIIT-NR} \hfill {\bf January 2017 - April 2017}\\
\vspace*{-.4cm}
\begin{list2}
\item[-] Compared Mamdani and Sugeno FIS for 13 input parameters and 6 output parameters for different input and
output Membership Functions using Fuzzy Logic. 
\item[-] Mathematically proved the correlation between the
different FISs and concluded with 9 inferences.
\end{list2}

\vspace{-.2cm}
\section{\sc Technical Abilities}
\begin{list2}
\item {\bf Languages}:  Python (Full-Stack), R, C/C++, MATLAB, JavaScript, SQL.
\item {\bf Libraries}: Keras, Tensorflow, NLTK, Scikit-learn, OpenCV, Pandas, Matplotlib, Flask.
\item {\bf Operating Systems}:  Windows: 7/8/10; Linux Distros.: Ubuntu, Kali; ROS.
\item {\bf Courses Completed}: Machine Learning, Advanced ML, Deep Learning, Artificial Intelligence.
% , IoT, Advance ML, Introduction to Big Data \& Cloud Computing, Big Data \& Cloud.
\end{list2}


\vspace{-0.1cm}
\section{\sc Extra-Curricular Activities}
\begin{list2}
% \vspace{-0.1cm}
\item {\bf Member of Core Team}: Technovate 2018 (Techno-Cultural Fest of IIIT-NR).
\item {\bf Member of Organizing Team}: Industry-Academia Meet 2017, IIIT-NR.
\item {\bf Head Organizer}: Connaissance 2016 (Literary cum Cultural Fest of IIIT-NR).
\item {\bf Zonal Coordinator}: Chimera X 2017 (Quiz Contest of MANIT Bhopal and ISTE).
\item {\bf Member of Mess Committee}: Raman House, IIIT-NR (January 2016 - August 2017).
\item {\bf 2nd Runner-up}: Breaking Bugs, Technovate 2017 (Code De-Bugging Competition).
\item {\bf Best Delegate}: Divya Jyoti National Youth Parliament 2017, Raipur.
\item {\bf Deputy Speaker - AIPPM}: Raipur International Diplomacy Summit 2016, Raipur.
\end{list2}

% \vspace{0.5in}
\section{\sc References}
\vspace{.01in}
\begin{tabular}{@{}p{2.5in}p{3in}}
{\bf Prof. John McCall} & {\it} {\bf Dr. Muneendra Ojha} \\ 
Head, School of CSDM & {\it} Assistant Professor, CSE \\
Robert Gordon University, Aberdeen, United Kingdom & {\it} International Institute of Information Technology, Naya Raipur, India\\
{\it E-mail:} j.mccall@rgu.ac.uk & {\it E-mail:} muneendra@iiitnr.edu.in \\
\end{tabular}

\vspace{-.1in}
\begin{tabular}{@{}p{3in}p{3in}}
{\bf Dr. Stewart Massie}\\
Senior Research Fellow, CSDM \\
Robert Gordon University, Aberdeen, \\
United Kingdom \\
{\it E-mail:} s.massie@rgu.ac.uk
\end{tabular}

\end{resume}
\end{document}
